### 2024-07-01 causal-inference.qmd
20240701 - clean up

#plot(YCausesX_alt) # this creates the same plot as above
ggdag::ggdag(YCausesX_alt)
```

@@

#plot(ZCausesXandY_alt) # this creates the same plot as above
ggdag::ggdag(ZCausesXandY_alt)
```

@@

plot(dagitty::graphLayout(mediationDag))

dagitty::impliedConditionalIndependencies(mediationDag)

@@

In this example, `X` influences `Y` via `M1` and `M2` (i.e., multiple mediatirs), and `M1` is also associated with `M2`.
The `dagitty::impliedConditionalIndependencies()` function identifies variables in the causal diagram that are conditionally independent (i.e., uncorrelated) after controlling for other variables in the model.
For this causal diagram, `X` is conditionally independent with `Y` because `X` is independent with `Y` when controlling for `M1` and `M2`.

@@

#plot(mediationDag_alt) # this creates the same plot as above
ggdag::ggdag(mediationDag_alt)
```

>>>>

#plot(YCausesX_alt) # this creates the same plot as above
ggdag::ggdag(YCausesX_alt) + theme_dag_blank()
```

@@

#plot(ZCausesXandY_alt) # this creates the same plot as above
ggdag::ggdag(ZCausesXandY_alt) + theme_dag_blank()
```

@@

plot(dagitty::graphLayout(mediationDag))
```

```{r}
dagitty::impliedConditionalIndependencies(mediationDag)

@@

In this example, `X` influences `Y` via `M1` and `M2` (i.e., multiple mediators), and `M1` is also associated with `M2`.
The `dagitty::impliedConditionalIndependencies()` function identifies variables in the causal diagram that are conditionally independent (i.e., uncorrelated) after controlling for other variables in the model.
For this causal diagram, `X` is conditionally independent with `Y` because `X` is independent with `Y` when controlling for `M1` and `M2`.

@@

#plot(mediationDag_alt) # this creates the same plot as above
ggdag::ggdag(mediationDag_alt) + theme_dag_blank()
```
